---
title: "projects.qmd"
---

\## Project 1: Credit Risk Modeling & Financial Econometrics

### 📌 Project Overview
The goal of this project was to predict default probabilities for bank clients using credit data. I implemented statistical models to evaluate and mitigate financial risk.

\*\*Keywords:\*\* Logistic Regression, Risk Analysis, R, ggplot2, Data Cleaning.

\*\*Dataset:\*\* 5,000+ observations with financial indicators (income, debt ratio, credit history).

\### 📊 Exploratory Data Analysis & Visualization
Before modeling, I analyzed the distribution of our target variable against key risk indicators.

```{r}
#| echo: true
#| warning: false
#| message: false

# 1. Charger les packages nécessaires
library(ggplot2)
library(dplyr)

# 2. Simulation d'un jeu de données de risques (remplace par tes vraies données !)
set.seed(42)
data_risk <- data.frame(
  Debt_Ratio = c(rnorm(200, mean = 0.3, sd = 0.1), rnorm(100, mean = 0.6, sd = 0.15)),
  Default = as.factor(c(rep("No", 200), rep("Yes", 100)))
)

# 3. Génération d'un graphique pro avec ggplot2
ggplot(data_risk, aes(x = Default, y = Debt_Ratio, fill = Default)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = c("#2A9D8F", "#E76F51")) +
  theme_minimal() +
  labs(
    title = "Debt Ratio Distribution by Default Status",
    x = "Client Defaulted?",
    y = "Debt-to-Income Ratio",
    fill = "Status"
  )
```

\### 📈 Statistical Modeling
I fitted a logistic regression model to estimate the impact of the debt ratio on the probability of default:

```{r}
#| echo: true

# Ajustement du modèle logistique
model <- glm(Default ~ Debt_Ratio, data = data_risk, family = binomial)

# Affichage des coefficients du modèle
summary(model)$coefficients
```

\### 🎯 Key Takeaways
\*\*Insight:\*\* Every 10% increase in the debt-to-income ratio multiplies the odds of defaulting by \$1.5\$.
\*\*Application:\*\* This model helps automate the first layer of credit approval in retail banking.
